---
title: "PortFolio5 - titanic"
author: "Martine Lind Jensen"
date: "28/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load packages 
library(pacman)
p_load(tidyverse, boot, lmerTest, caret, e1071)
```

```{r}
#Loading data 

titanic <- read.csv("titanic.csv")

#titanic <- titanic[,-6]
```

Creating a logistic model tgat predicts survival of gender, age and class 

```{r}
titanicm <- glm(Survived ~ Sex + Age + Pclass, titanic, family = binomial)
summary(titanicm)
#And what you can see in the summary is that the intercept female class 1. So if you want to find a male class 1, you subtract the sexmale from the intercept. 

```


Creating a logistic model that predicts survival(1) of gender
```{r}
genderm <- glm(Survived ~ Sex, titanic, family = binomial)
summary(genderm)

titanic$Survived <- as.factor(titanic$Survived)
levels(titanic$Survived)

#log odds into probability for estimate of intercept female (the probability being 1)
boot::inv.logit(1.0566)

#log odds into probability for estimate of going from female to male
boot::inv.logit(1.0566 - 2.5051)
```


Creating a logistic model that predicts survival(1) from class 
```{r}
classm <- glm(Survived ~ Pclass, titanic, family = binomial)

summary(classm)

titanic$Pclass <- as.factor(titanic$Pclass)

#log odds into probability for estimate of intercept (the probability being 1) surviving people on class 1
boot::inv.logit(0.5306)

#log odds into probability for estimate of going from class 1 to class2 surviving people on class 2 
boot::inv.logit(0.5306 - 0.6394)


#log odds into probability for estimate of going from class 1 to class2 to class3 surviving people on class 3
boot::inv.logit(0.5306 - 1.6596)
```

Creating a logistic model that predicts the survival(1) of the median age of females and of males 

```{r}

age_sex <- glm(Survived ~ Age + Sex, titanic, family = binomial)

summary(age_sex)

#For males median age of 28. So this thing takes the intercept(females) subtract the slope of males and takes the median age for males times the age slope 
boot::inv.logit(1.113881 - 2.500001 + median(titanic[titanic$Sex == "male",]$Age) * (-0.002060))


#For males median age of 27. So this thing takes the intercept(females) and takes the median age for females times the age slope 
boot::inv.logit(1.113881 + median(titanic[titanic$Sex == "male",]$Age) * -0.002060)
```

#### Train and test data

Let's see how our model performs when we do it more properly: train model on one set of data and testing on the other one. In future, you will learn to split data in a better way, making sure both training and testing data is representative of all categories. For now, just dividing by the id is fine.

```{r}
#make id numeric, so we can use it to split the data
titanic$Name <- as.numeric(titanic$Name)


#everyone with id below 30 - train data, above 30 - test data
titanic_train <- subset(titanic, Name < 444) #training data
titanic_test <- subset(titanic, Name > 444) #test data

#fit model to train data
trained_model <- glm(Survived ~ Sex + Age + Pclass, titanic_train, family = binomial)

#predict values in test data
predicted_probs_test = predict(trained_model, titanic_test, type = 'response')

#extract actual shape categories, i.e. 'true answers' from the original dataframe
actual_categories_test = titanic_test$Survived

#make a dataframe to see predicted probabilities of jagged category against the actual category
pred_df_test <- tibble(predicted_probs_test, actual_categories_test)


#make a new column to see more easily what our model predicted: if probability is less than 0.5 - it predicted 'curved', otherwise - it predicted jagged
pred_df_test$predicted_category = ifelse(pred_df_test$predicted_probs_test < 0.5, 0, 1)

#let's see first 6 rows
head(pred_df_test)

#make sure predicted category is a factor (at the moment it's a character variable due to the way we specified ifelse outcomes)
pred_df_test$predicted_category <- as_factor(pred_df_test$predicted_category)

#make the confusion matrix
confusionMatrix(pred_df_test$predicted_category, pred_df_test$actual_categories_test, positive = "1")

```
